\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
\markboth{Preface}{}%I don't know why, but the author says so: to let me put empty brackets here.

\section{Is This Handout for You?}
This handout is created to help students understand calculus with stress on computation techniques rather than rigorous proofs. The goal is to present the material clearly and organized, making it easier to follow and apply in practical problems.


The main focus will be on solving problems effectively using methods from differentiation and integration rather than delving into the theoretical foundations of calculus. 
\section{What's in This Handout?}

Throughout this handout, I have reorganized the content in a way that I believe will help students learn the topics more logically. The sequence is designed to build from basic concepts to more complex ones, allowing for a smoother learning experience.


The abstract of this course is mentioned below, which will serve as
a roadmap for you to gain the essence of calculus.
\begin{introduction}[Core concept]
    \item Limits and Continuity
    \item Derivatives
    \item Integrals
    \item Series
\end{introduction}

\section{How to Read this Handout?}
\begin{itemize}
    \item Do examine the given conditions carefully! Mostly, they are as important as the conclusion of a theorem.
    \item Refer the other books if you find some of the content looks hard to understand. (This is also practical when you are reading any other math books)
\end{itemize}




I hope this handout serves as a helpful guide for students looking to strengthen their calculation abilities and build a strong foundation in calculus.